%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%                                                                 %
%                         ACKNOWLEDGEMENT                         %
%                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
 
\specialhead{ACKNOWLEDGMENT}
I still remember that evening on August 11th, 2011 when I landed in JFK international airport. The moment that I made my first step out of the cabin, I was greeted by a big smile from a ground staff. ``Welcome to America!'', I heard. I smiled back, and replied with a ``Thank you!'' in a reduced Chinese accent (I practiced a lot to imitate the American accent). I was super excited at that time, because I knew that I would open up a brand new chapter in my life. 

On the very night before my flight, my parents were sleepless. Their 23-year-old boy was flying to the other side of the earth. It is a country that they only saw and heard from international news and Hollywood blockbusters. Of course they were worried, even though I was already a grown-up. I was always the kid in their eyes, regardless of my age.

Both my father Kexue Yan and mother Xiaodan Hou are forever the most important people to me. They gave my life to me, taught me how to speak, walk and run, accompanied me with the family warmth, educated me to become a useful person, supported me from all the aspects, and shaped me as who I am now. Mom and Dad, what I really wanted to tell you is that I have been working and will always work hard to become your pride, although I know that I am already your pride no matter what. I love you!   

Love at first sight is not what I believed until I met you, Sihui Li. It was a nice August morning at Beijing capital international airport, and I saw you walking towards me while pushing a baggage cart. You were in a red striped T-shirt and white shorts, combed your bangs up. You looked so cute that I just cannot move my eyes away from you. When you saw me staring at you, you subconsciously shifted your gaze, but your face turned blushing. I stepped forward and said hi. You smiled back, and my heart was literally melted.  I am a lucky man, since the girl who I love also loves me. Every single second that we've been together is so sweet and worth remembering. I love you! 

Prof. Deborah L. McGuinness is my respected and beloved academic advisor. 
I didn't make an appointment with her before I knocked on her door for the first time. 
She wasn't offended, but asked me to come in. 
I timidly expressed my intention to work with her. 
From then on, I became her six-th PhD student at RPI.
During my entire PhD student career, Dr. McGuinness provided the maximum freedom for me to learn and explore.
She is considerate and often asks me to get enough sleep.
She is responsible and revises all my papers in detail.
She is strict and makes sure that I do good research, speak and write proper English.
She is strong both mentally and physically. 
She is optimistic and encourages me a lot. 
She is knowledgeable and helped a lot for my research. 
She is like a light house in the dark, always illuminating the way I sail.
Being able to work with Dr. McGuinness is among the best experiences I've ever had.
Thank you, Deborah!

Dr. Mark Greaves is my external committee member. 
This thesis wouldn't be possible without his tremendous help. 
I really appreciate the two-year collaboration with Dr. Greaves and Pacific Northwest National Laboratory, which is the period when I have most of my dissertation done.
Dr. Greaves provided lots of insightful idea that inspired me on my thesis topic. 
He is deeply involved in my research papers and gave me many constructive reviews.
He is smart, supportive, patient, generous, and considerate.
Thank you, Mark!

Prof. James Hendler, Prof. Peter Fox, and Prof. Emanuele Della Valle are my thesis committee members. 
I have benefited a lot from the courses that Dr. Hendler and Dr. Fox have taught.
All the juicy and useful feedback that was provided by you to this dissertation really helped shape this dissertation.
Dr. Della Valle is the inventor of the stream reasoning domain.
His research work has laid a firm foundation upon which I built this thesis.
Thank you, Jim, Peter, and Emanuele!

I really enjoyed my seven years at RPI and six years at Tetherless World Constellation. 
I would like to thank Ms. Jacky Carley and Ms. Melissa Anderson for their help.
I would like to thank Mr. William Smith and Dr. Brenda Praggastis for their help on my research.
I would like to thank all my labmates and friends. 
We had lots of fantastic useful/useless academic/non-academic discussions, game parties and soccer matches!
I wanted to thank all the people who has helped me during my entire life!

With this PhD thesis, I have officially finished up this chapter in my life.
I really want to thank myself, for my perseverance and hard work. 
A brand new chapter awaits to be written!
Keep calm and change the world! Why not?

% committee members:
% family: father, mother, grandma
% friends: sihui li, xin lin, zehao yang, lai jiang, jiamin ni, jubiao yang, xin shen, ying lu, han wang, hui li, dapeng zhang, yu xia, siqi nie, yan ou, quan wang, yanning chen, ziheng wang, xiaoyang wang, qi zhou, yiming gao, linyun fu, ping wang
% collaborators: liyu pan, litie zhu, yi xie, james mccusker, amar, katie, zhicheng liang, yue liu, kristine
% lab staff: jacky, terry, melisa
% heu: xiufen ye, hongwei mo, kejun wang, xianye ben, ji'er xi, ling zhu, jianan wang, yixin zhang, caihong xue, zhonghang geng, chen liang, zheng qu, qiuyan miao, ningbin huang
% elementary school: haiyang xu, shuai wang, chunyu feng, chuang guan, wenhe wang, haopeng wang
% middle school: yang chu, yang bai, shuyang zhang, fulong luo
% high school: yu wang, li qing
% shenqing: xianshui cao, zhe yu